---
title: "Analysis and Results"
execute:
  echo: false
  message: false
format: 
  docx:
    toc: true
    number-sections: true
bibliography: references.bib
csl: apa.csl
---

```{r}
#| message: false

library(groundhog)

groundhog_day <- "2024-03-01"

groundhog::meta.groundhog(groundhog_day)

groundhog::groundhog.library(
  "
library(here)
library(marginaleffects)
library(lmtest)
library(sandwich)
library(gtsummary)
library(tidyverse)
  ", date = groundhog_day
)

dat <- readRDS(
  file = here::here("01_data-processing", "data", "data_final.rds")
)

models <- readRDS(
  file = here::here("02_analysis-codes", "outputs", "models.RDS")
)

# total number of posts
n_posts <- nrow(dat)
```

# Method

Data was collected from 9 leading Israeli universities' public Facebook pages, using CrowdTangle software [@aboutus] to extract and mine data. This enabled us to export all data and information from the universities official Facebook pages, including user responses, engagement rates, and reactions.

Each page's data was converted into a CSV file, with each sheet representing a different page. The timeframe of this sample was initially started on Oct 7th in response to the massacre and terminated within the \_\_ months post the starting of the war. TO ADD: HOW WERE THE FILES ADDED TOGETHER TO CREATE THE FINAL CSV?

## Measures

We were interested in how the number and kind (positive / negative) of interactions to posts were related to the university and the category of post, and therefore created the following measures:

### **Post Category** 

Posts were manually categorized into one of 5 categories: "Community Support", "Updates and Instructions", "Academic Adjustments", "Supporting Our Troops and Hostages", and "Marketing of Academic Programs".

### **Total Interaction**

Total interaction was measured using the sum of interactions, such as likes, shares, reactions, and comments, on a page, which is consistent with previous studies [@eberl2020].

### **Positive Sentiment**

Positive sentiment was calculated for each post by adding the number of positive reactions, namely "Likes", "Love", and "Care" reactions.

### **Negative Sentiment**

Negative sentiment was calculated for each post by adding the number of negative reactions, namely the "Sad" and "Angry" reactions.

# Results

## Descriptives

We collected `r n_posts` posts from the 9 Universities included in the sample. @tbl-n_posts shows the total number of posts in each category created within each University's Facebook page, as well as the total number of posts for each University. We can see that all universities had over 70 posts in this period, with Bar-Ilan University topping the chart with 128 post.

```{r}
#| label: tbl-n_posts
#| tbl-cap: Number of posts in sample by University and Category

tab_n <- readRDS(here::here("02_analysis-codes", "outputs", "table_n.rds"))

rempsyc::nice_table(tab_n, separate.header = TRUE, italics = seq(tab_n))
```

Examining the descriptive statistics by University, as presented in @tbl-uni, we see clear signs of overdispersion (the standard deviation of each count is clearly higher than the mean). The same can be observed when we calculate descriptive statistics for each category instea, as in @tbl-cat. More descriptive analyses, including simple visualizations of the raw data itself, are available at (ADD LINK OR EXPLAIN GITHUB REPOSITORY).

```{r}
#| label: tbl-uni
#| tbl-cap: Descriptives for interactions by University

tab_uni <- readRDS(here::here("02_analysis-codes", "outputs", "table_uni.rds"))

rempsyc::nice_table(tab_uni, separate.header = TRUE, italics = seq(tab_uni))
```

```{r}
#| label: tbl-cat
#| tbl-cap: Descriptives for interactions by Post Category

tab_cat <- readRDS(here::here("02_analysis-codes", "outputs", "table_cat.rds"))

rempsyc::nice_table(tab_cat, separate.header = TRUE, italics = seq(tab_cat))
```

# References