---
title: "Analysis and Results"
execute:
  echo: false
  message: false
format:
  docx:
    toc: false
  html:
    toc: true
bibliography: references.bib
csl: apa.csl
---

```{r}
#| message: false

library(groundhog)

groundhog_day <- "2024-03-01"

groundhog::meta.groundhog(groundhog_day)

groundhog::groundhog.library(
  "
library(here)
library(marginaleffects)
library(lmtest)
library(sandwich)
library(gtsummary)
library(tidyverse)
  ", date = groundhog_day
)

dat <- readRDS(
  file = here::here("01_data-processing", "data", "data_final.rds")
)

models <- readRDS(
  file = here::here("02_analysis-codes", "outputs", "models.RDS")
)

# total number of posts
n_posts <- nrow(dat)
```

# Method

Data was collected from 10 leading Israeli universities' public Facebook pages, using CrowdTangle software [@aboutus] to extract and mine data. This enabled us to export all data and information from the universities official Facebook pages, including user responses, engagement rates, and reactions.

Each page's data was converted into a CSV file, with each sheet representing a different page. The timeframe of this sample was initially started on Oct 7th in response to the massacre and terminated within the \_\_ months post the starting of the war. TO ADD: HOW WERE THE FILES ADDED TOGETHER TO CREATE THE FINAL CSV?

## Measures

We were interested in how the number and kind (positive / negative) of interactions to posts were related to the university and the category of post, and therefore created the following measures:

### Post Category

Posts were manually categorized into one of 5 categories: "Community Support", "Updates and Instructions", "Academic Adjustments", "Supporting Our Troops and Hostages", and "Marketing of Academic Programs".

### Total Interaction

Total interaction was measured using the sum of interactions, such as likes, shares, reactions, and comments, on a page, which is consistent with previous studies [@eberl2020].

### Positive Sentiment

Positive sentiment was calculated for each post by adding the number of positive reactions, namely "Likes", "Love", and "Care" reactions.

### Negative Sentiment

Negative sentiment was calculated for each post by adding the number of negative reactions, namely the "Sad" and "Angry" reactions.

## Analysis

All statistical analyses were conducted with R [@rcoreteam2024] version 4.3.3 and RStudio [@rstudio2024] version 2023.12.1.402. All data and code are available at XXX.

Our inferential analysis relies on a series of generalized linear models. To account for potential overdispersion in each of our count outcomes (total interactions, positive sentiment, negative sentiment), we used quasi-poisson models with robust standard errors [@wooldridge2002]. For ease of interpretation, we then used the models to create predictions on the response scale (e.g., the number of interactions) for our different groups of interest and plotted means and uncertainty of those predictions.

TO DO: Cite all the packages used in the analysis.

# Results

## Descriptives

We collected `r n_posts` posts from the 9 Universities included in the sample. @tbl-n_posts shows the total number of posts in each category created within each University's Facebook page, as well as the total number of posts for each University. We can see that all universities had over 70 posts in this period, with Bar-Ilan University topping the chart with 128 post.

```{r}
#| label: tbl-n_posts
#| tbl-cap: Number of posts in sample by University and Category

tab_n <- readRDS(here::here("02_analysis-codes", "outputs", "table_n.rds"))

rempsyc::nice_table(tab_n, separate.header = TRUE, italics = seq(tab_n))
```

Examining the descriptive statistics by University, as presented in @tbl-uni, we see clear signs of overdispersion (the standard deviation of each count is clearly higher than the mean).

```{r}
#| label: tbl-uni
#| tbl-cap: Descriptives for interactions by University

tab_uni <- readRDS(here::here("02_analysis-codes", "outputs", "table_uni.rds"))

rempsyc::nice_table(tab_uni, separate.header = TRUE, italics = seq(tab_uni))
```

The same can be observed when we calculate descriptive statistics for each category instead, as in @tbl-cat. More descriptive analyses, including simple visualizations of the raw data itself, are available at (ADD LINK OR EXPLAIN GITHUB REPOSITORY).

```{r}
#| label: tbl-cat
#| tbl-cap: Descriptives for interactions by Post Category

tab_cat <- readRDS(here::here("02_analysis-codes", "outputs", "table_cat.rds"))

rempsyc::nice_table(tab_cat, separate.header = TRUE, italics = seq(tab_cat))
```

## Inferential analysis

In this section, we highlight the model results most relevant to our research questions. A full inferential report with further results is available at XXX. We will look at the following questions in order:

-   How do total interactions to posts vary by university?

-   How do total interaction to posts vary by post category?

-   How do positive interactions to posts vary by post category?

-   How do negative interaction to posts vary by post category?

### Total Interaction

#### How do total interactions vary by university?

Using our quasi-poisson model predicting total interactions as a function of university, we generate predictions for total interactions across the dataset and marginalize over the different universities. The results, presented in @tbl-total-uni, show that the University of Haifa has the most interactions and Bar-Ilan University the least.

```{r}
#| label: tbl-total-uni
#| tbl-cap: Average predictions for total interactions by university

marginaleffects::avg_predictions(
  model = models$total_uni,
  by = "university",
  vcov = "HC3"
) |> 
  dplyr::select(-c(rowid, s.value, p.value, rowid_dedup)) |> 
  rempsyc::nice_table()
```

We compute pairwise differences to evaluate which universities receive significantly more (or fewer) interactions that the others. For brevity, @tbl-total-uni-pairs below displays all the significant estimates for pairwise differences. For the unabridged table and accompanying plots, see XXX.

```{r}
#| label: tbl-total-uni-pairs
#| tbl-cap: Significant pairwise differences for total interactions by university

marginaleffects::avg_predictions(
  model = models$total_uni,
  by = "university",
  hypothesis = "pairwise",
  type = "response",
  vcov = "HC3"
) |> 
  dplyr::select(-c(s.value)) |> 
  dplyr::filter(p.value < .05) |> 
  rempsyc::nice_table()
```

#### How do total interactions vary by post category?

Using our quasi-poisson model predicting total interactions as a function of post category, we generate predictions for total interactions across the dataset and marginalize over the different categories. The results, presented in @tbl-total-cat, show that "Supporting Our Troops and Hostages" has the most interactions and "Updates and Instructions" the least.

```{r}
#| label: tbl-total-cat
#| tbl-cap: Average predictions for total interactions by category

marginaleffects::avg_predictions(
  model = models$total_cat,
  by = "category",
  vcov = "HC3"
) |> 
  dplyr::select(-c(rowid, s.value, p.value, rowid_dedup)) |> 
  rempsyc::nice_table()
```

We compute pairwise differences to evaluate which categories receive significantly more (or fewer) interactions that the others and present results in @tbl-total-cat-pairs below. All differences are significant except for those between the categories "Updates and Instructions", "Marketing of Academic Programs", and "Academic Adjustments". Posts in the category "Supporting our Troops and Hostages" received significantly more interactions than posts in any other category.

```{r}
#| label: tbl-total-cat-pairs
#| tbl-cap: Pairwise differences for total interactions by category

marginaleffects::avg_predictions(
  model = models$total_cat,
  by = "category",
  hypothesis = "pairwise",
  type = "response",
  vcov = "HC3"
) |> 
  dplyr::select(-c(s.value)) |> 
  rempsyc::nice_table()
```

### How do positive interactions vary by post category?

Using our quasi-poisson model predicting positive sentiment as a function of post category, we generate predictions for positive sentiment across the dataset and marginalize over the different categories. The results, presented in @tbl-pos-cat, show that "Supporting Our Troops and Hostages" has the most interactions and "Updates and Instructions" the least.

```{r}
#| label: tbl-pos-cat
#| tbl-cap: Average predictions for positive sentiment by category

marginaleffects::avg_predictions(
  model = models$pos_cat,
  by = "category",
  vcov = "HC3"
) |> 
  dplyr::select(-c(rowid, s.value, p.value, rowid_dedup)) |> 
  rempsyc::nice_table()
```

We compute pairwise differences to evaluate which categories receive significantly more (or fewer) interactions that the others and present results in @tbl-pos-cat-pairs below. The category "Supporting our Troops and Hostages" receives more positive interactions that the rest, but not significantly more than "Community Support".

```{r}
#| label: tbl-pos-cat-pairs
#| tbl-cap: Pairwise differences for positive sentiment by category

marginaleffects::avg_predictions(
  model = models$pos_cat,
  by = "category",
  hypothesis = "pairwise",
  type = "response",
  vcov = "HC3"
) |> 
  dplyr::select(-c(s.value)) |> 
  rempsyc::nice_table()
```

### How do negative interactions vary by post category?

Using our quasi-poisson model predicting negative sentiment as a function of post category, we generate predictions for negative sentiment across the dataset and marginalize over the different categories. The results, presented in @tbl-neg-cat, show that "Supporting Our Troops and Hostages" has the most interactions and "Updates and Instructions" the least. We can also see that categories other than "Supporting Our Troops and Hostages" receive a comparatively negligible amount of negative interactions.

```{r}
#| label: tbl-neg-cat
#| tbl-cap: Average predictions for negative sentiment by category

marginaleffects::avg_predictions(
  model = models$neg_cat,
  by = "category",
  vcov = "HC3"
) |> 
  dplyr::select(-c(rowid, s.value, p.value, rowid_dedup)) |> 
  rempsyc::nice_table()
```

We compute pairwise differences to evaluate which categories receive significantly more (or fewer) interactions that the others and present results in @tbl-neg-cat-pairs below. The category "Supporting our Troops and Hostages" receives more negative interactions that all other categories, and "Community Support" posts receive significantly more negative interactions than "Academic Adjustments" posts, but this difference is small at 7.36 more negative interactions (95% CI\[0.05, 14.67\]).

```{r}
#| label: tbl-neg-cat-pairs
#| tbl-cap: Pairwise differences for negative sentiment by category

marginaleffects::avg_predictions(
  model = models$neg_cat,
  by = "category",
  hypothesis = "pairwise",
  type = "response",
  vcov = "HC3"
) |> 
  dplyr::select(-c(s.value)) |> 
  rempsyc::nice_table()
```

# References
