---
title: "Analysis and Results"
execute:
  echo: false
  message: false
format: 
  docx:
    toc: true
    number-sections: true
bibliography: references.bib
---

```{r}
#| message: false

library(groundhog)

groundhog_day <- "2024-03-01"

groundhog::meta.groundhog(groundhog_day)

groundhog::groundhog.library(
  "
library(here)
library(marginaleffects)
library(lmtest)
library(sandwich)
library(gtsummary)
library(tidyverse)
  ", date = groundhog_day
)

dat <- readRDS(
  file = here::here("01_data-processing", "data", "data_final.rds")
)

models <- readRDS(
  file = here::here("02_analysis-codes", "outputs", "models.RDS")
)

# total number of posts
n_posts <- nrow(dat)
```

# Method

Data was collected from 9 leading Israeli universities' public Facebook pages, using CrowdTangle software [@aboutus] to extract and mine data. This enabled us to export all data and information from the universities official Facebook pages, including user responses, engagement rates, and reactions.

Each page's data was converted into a CSV file, with each sheet representing a different page. The timeframe of this sample was initially started on Oct 7th in response to the massacre and terminated within the \_\_ months post the starting of the war. TO ADD: HOW WERE THE FILES ADDED TOGETHER TO CREATE THE FINAL CSV?

## Measures

We were interested in how the number and kind (positive / negative) of interactions to posts were related to the university and the category of post, and therefore created the following measures:

### **Post Category** 

Posts were manually categorized into one of 5 categories: "Community Support", "Updates and Instructions", "Academic Adjustments", "Supporting Our Troops and Hostages", and "Marketing of Academic Programs".

### **Total Interaction**

Total interaction was measured using the sum of interactions, such as likes, shares, reactions, and comments, on a page, which is consistent with previous studies [@eberl2020].

### **Positive Sentiment**

Positive sentiment was calculated for each post by adding the number of positive reactions, namely "Likes", "Love", and "Care" reactions.

### **Negative Sentiment**

Negative sentiment was calculated for each post by adding the number of negative reactions, namely the "Sad" and "Angry" reactions.

# Results

We collected \`r n_dat\` posts from the 9 Universities included in the sample. Table 1 shows the total number of posts in each category created within each University's Facebook page.

NOTE: Consider making the table shorter and wider, giving each category a column so each uni only needs one row.

```{r}
tab_n <- readRDS(here::here("02_analysis-codes", "outputs", "table_n.rds"))

rempsyc::nice_table(tab_n, separate.header = TRUE, italics = seq(tab_n))
```

Table 1 indicating the following descriptive variables: University, number of followers, total interactions, positive and negative sentiment averages per page.
